---
title: "Soil Textural Cluster"
author: Leo Jude D. Villasica
---

## Packages Needed

Here are the list of packages need to make a soil textural diagram

-   `soiltexture` - Need for the triangulation of soil texture data (clay, silt and sand)

-   `scales` - for proper scaling of the graph

-   `googlesheets4`  - for importing data from Google sheets directly

```{r}
library(soiltexture)
library(scales)
library(googlesheets4)
```

## Import of Data

For this part, we will be using the package `googlesheets4` using `range_read`

```{r}
ggsheet <- data.frame(range_read("https://docs.google.com/spreadsheets/d/1V-azZSYL14cvC5lrXtQ7lI17cSHOsWm1H82nbC6jRNE/edit#gid=71192194", sheet = "San Miguel Clean"))
```

## Creation of the Textural Diagram and Adding Data

```{r}
TT <- TT.plot(
  class.sys = "USDA.TT",    # use "our" texture triangle
  main = "Soil Texture Cluster",          # title
  tri.sum.tst = FALSE,            # do not test for exact sum(sand, silt, clay) == 100
  cex.lab = 0.75,                 # scaling of label text
  cex.axis = 0.75,                # scaling of axis
  frame.bg.col = 'white',         # background color
  class.lab.col = 'black',        # color for texture class labels
  lwd.axis = 1.5,
  lwd.lab = 2,
  arrows.show=TRUE
)

xy <- TT.points(tri.data = ggsheet, geo = TT, tri.sum.tst = FALSE, cex=0.5, col=alpha('royalblue', 0.5))
```
